% !TEX root = ../../main.tex

\section{Introduction}

Historically, the processing of isotherms was done by hand, with large
worksheets being used for the calculations. As an example,
it can be pointed out that one of the initial limitations of the
Barrett-Joyner and Halenda method for determining pore size distribution
was that each point had to be estimated with an approximation of critical
pore radius, resulting in tedious 
work~\cite{barrettDeterminationPoreVolume1951}.

The advent of computers meant that calculations could be performed
quickly and reliably and led to the development of more computationally
demanding methods for adsorption modelling and isotherm processing, such 
as the \gls{DFT} and \gls{GCMC} kernel fitting methods for pore size 
distribution~\cite{seatonNewAnalysisMethod1989,%
	tarazonaPhaseEquilibriaFluid1987}.
Commercial adsorption equipment which offers the users
a complete software solution for any isotherm calculations is now
commonplace, and makes obtaining reports of desired properties
for measured materials a matter of seconds.

Given the current ubiquity of adsorption as a characterisation method,
particularly for investigating surfaces and porous compounds,
there is a large pool of data published in the scientific community.
Recent efforts have focused on building a database of adsorption
isotherms~\cite{sideriusNISTARPAEDatabase2015}, to offer a searchable
pool of standardised behaviours on different materials. This serves as
both a useful reference for comparing newly synthesised compounds, 
as well as a method for scoping materials which have the
required properties for a desired application.

The abundance of data reflects a trend in recent years where, due
to the prevalence of digital records and cheap storage, more
information is available than ever before. As such, challenges
now lie in making sense of the so called ``big data''.
\gls{KPI} such as specific surface area, working
capacity and pore volume are commonly reported in scientific literature
and used as benchmarking tools. Furthermore,
several studies have attempted to find a reliable indicator for
the suitability of an adsorbent for a specific
application~\cite{regeSimpleParameterSelecting2001, %
	ackley2000psa,%
	wiersumAdsorbentPerformanceIndicator2013} such as pressure swing
adsorption.

However, we feel that a critical step in the process has yet
to be fully addressed. Transitioning from measured isotherms
to the calculation of such \gls{KPI} requires individual
implementation of previously mentioned techniques or the use of 
``black box'' apparatus. As such,
not only can errors arise in the implementation, but
a critical survey of a large body of results is between time consuming
and impossible. In conclusion, a standardised method of high throughput
processing of such data would be invaluable not only for reference purposes,
but also for in-depth studies of data reliability,
structure-property relationships and effect of different variables on
the adsorption properties of a material.

\subsection*{Chapter summary}

In this chapter an open-source software package is presented, which
is released under an MIT licence and written in Python, intended to be
used for manipulation, storage, visualisation and processing of
adsorption isotherms. The software is aimed to give users a powerful
yet easy to use package that can determine the kind of \gls{KPI}
common to adsorption methodology, while using large datasets of hundreds
or thousands of isotherms. The code is then used to process a
dataset of 26 000 isotherms from the \gls{NIST} adsorption database in order
to highlight the variability of adsorption data reported in literature
on \glspl{MOF}.

\subsection*{Contributions}

Paul Iacomi wrote the python code for the pyGAPS framework and is
responsible for its publication and maintenance as an open source
package. The \gls{IAST} functionality is a modified version of
the pyIAST code, published by Cory 
Simon~\cite{simonPyIASTIdealAdsorbed2016}. The DFT kernel 
provided with pyGAPS was calculated by Renaud Denoyel. 
Example data on reference materials was recorded by Paul Iacomi 
for Takeda 5A and UiO-66(Zr) and by Emily Bloch on MCM-41 and
porous silica. The bulk processing
example data comes from the \gls{NIST} Adsorption Database, 
maintained by Dan Siderius.
