% !TEX root = ../../main.tex

\section{Introduction}

Until this chapter, it has been assumed that the porous materials 
remain rigid when adsorbing a gas. Differences in pore size, crystalinity 
or structure may exist, but these properties are assumed not to change
as the host fluid enters the pores.
In most cases this is a reasonable supposition. However, it is not 
universally applicable, as the forces and interactions exerted 
during adsorption may induce changes in solid itself.

Such effects in classic porous inorganic materials like zeolites, carbons 
and clays take the form of structural contraction and expansion, swelling
or counterion displacement~\cite{coudertMolecularInsightCO2017}.
It is only recently that flexibility was discovered in coordination
polymers, such as MOFs. A feature which arises from 
their comparatively weak coordination bonds or pliant organic components,
it allows for a systematic deflection of bonds throughout the 
entire crystal lattice.
As such, the term ``soft porous crystal'' defines porous solids that are 
both highly ordered and possess the ability to reversibly transform
their structure upon external stimuli. Part of the so-called
third generation of crystalline porous compounds, they represent 
some of the latest developments in the field of MOFs.

The unique properties of flexible materials can preclude
their application in fields such as sensing, micromechanical
devices and highly efficient gas storage. It is these perspectives
that make their synthesis and design a key research interest.
However, their flexible nature introduces new challenges in
their characterisation, as factors such as temperature and
thermal history~\cite{liuReversibleStructuralTransition2008},
crystal size~\cite{zhangCrystalSizeDependentStructuralTransitions2014, %
krauseEffectCrystalliteSize2018}, external 
pressure~\cite{itoReversiblePoreSize2013, %
chanutUsingExternalFactors2016}, structural defects~\cite{bennettInterplayDefectsDisorder2016} 
and even adsorption kinetics play a role in their compliance.
This type of variability goes beyond what has been insofar discussed
in this thesis and it is here where a combined characterisation approach
becomes essential in understanding the fundamental physics
governing flexibility and prediction of adsorption behaviour.
In this chapter, a study of the differential enthalpy of adsorption
on DUT-49, a soft coordination polymer,
measured directly through calorimetric methods as detailed in 
\autoref{calo}, will be seen to shed light on the source of 
flexibility and the effectiveness of different avenues for its
control.

\subsection*{Summary}

After a brief introduction of the background of soft porous 
materials, this chapter will present the characterization of a novel
flexible MOF (DUT-49) and its analogues. This material undergoes
a sudden contraction of its unit cell into a lower volume state
upon adsorption, resulting in the expulsion of gas from its pores.
This phenomena was coined ``negative gas adsorption'' (NGA).
The text will focus on characterisation through calorimetric methods
performed by Paul Iacomi, together with references
of results obtained by collaborating groups, included in order
obtain a complete story of the underlying mechanism behind NGA.

\subsection*{Contribution}

The synthesis of all MOFs was performed by Simon Krause
(TU Dresden), together with their initial characterization through 
nitrogen adsorption at \SI{77}{\kelvin}.
Ambient and low temperature calorimetry was carried out by 
Paul Iacomi. Computer simulations of adsorption isotherms, 
linker buckling and structural contraction
are the result of work from Jack Evans and Dr.\ F.X Coudert.
Mechanical compression experiments were performed in 
the group of Prof.\ Guillaume Maurin in Montpellier. \todo{neutron methods}
Dr.\ Philip Llewellyn and Prof.\ Stefan Kaskel were 
instrumental in the interpretation of the results obtained.
