% !TEX root = ../main.tex

\chapter{Contributions}

The results in this thesis have been obtained in collaboration
with various groups and universities. This page will list 
individual contributions to any presented data.

{\setstretch{1}
\textbf{Chapter 1}
\begin{itemize}
    \small
    \item pyGAPS is written and distributed by Paul Iacomi. IAST 
    functionality comprised within is a modified version of the pyIAST 
    code by Corey Simon. The framework depends on multiple open source
    packages such as Coolprop, numpy, pandas, scipy, matplotlib.
    \item The NIST database is created and maintained by Dr. Dan Siderius.
\end{itemize}

\textbf{Chapter 2}
\begin{itemize}
    \small
    \item The UiO-66(Zr) gravimetric isotherms were recorded by 
    Andrew Wiersum. Calorimetric data was recorded by Paul Iacomi.
    \item The Takeda 5A calorimetric dataset was recorded and processed by Paul Iacomi.
    \item The Zr Fumarate calorimetric dataset, TGA data, \ce{H2O} isotherms and propane/propylene isotherms were recorded and 
    processed by Paul Iacomi. 
\end{itemize}

\textbf{Chapter 3}
\begin{itemize}
    \small
    \item Initial batches of UiO-66(Zr) were synthesised by Paul Iacomi, Joao Marreiros, Giel Arnauts and Wouter Arts. Further batches were
    synthesised and leached by Joao Marreiros.
    \item XRD data was recorded by Joao Marreiros.
    \item TGA, nitrogen physisorption and \ce{CO2} adsorption were performed by Paul Iacomi, together with data processing.
\end{itemize}

\textbf{Chapter 4}
\begin{itemize}
    \small
    \item UiO-66 and MIL-100 synthesis took place in the group of Prof.\ Jong-San Chang, KRICT. MIL-127 synthesis was performed in the group
    of Dr.\ Christian Serre.
    \item All shaping through granulation was performed in the group of
    Prof.\ Jong-San Chang.
    \item Paul Iacomi recorded all calorimetry isotherms, TGA data,
    nitrogen physisorption and vapour sorption data, as well as 
    performed the processing. 
\end{itemize}

\textbf{Chapter 5}
\begin{itemize}
    \small
    \item Synthesis of all DUT-49 and derivatives was performed by 
    Simon Krause and collaborators.
    \item Calorimetry at \SI{77}{\kelvin} and \SI{303}{\kelvin} was
    performed by Paul Iacomi.
    \item \textit{In situ} neutron powder diffraction and simulations
    for \ce{CD4} adsorption are the result of work by Simon Krause, 
    Jack Evans and collaborators.
    \item Variation of NGA with temperature and adsorbate was recorded
    by Simon Krause.
    \item All other data processing is performed by Paul Iacomi.
\end{itemize}
}