% !TEX root = ../../main.tex

\section{Synthesis, shaping and characterisation}

\subsection{Material Synthesis}

The synthesis of these MOFs is well described in literature,
as it has been previously reported for
UiO-66(Zr)~\cite{cavkaNewZirconiumInorganic2008} and
MIL-100(Fe)~\cite{YangWaterStableMetalOrganic2013}.

The UiO-66(Zr) and MIL-100(Fe) powders have been synthesised at the
Korea Research Institute of Chemical Technology (KRICT) according
to the methods previously referenced. Complete details of the
synthesis method can be found in the related
publication~\cite{valekarShapingPorousMetal2017}
and in Appendix~\ref{appx:synthesis}.

\subsection{Shaping Procedure}

The shaping of the samples also took place at KRICT and was done
using a wet granulation method. In the case of the alumina binder,
the MOF powder was was mixed with the previously prepared mesoporous
\(\rho\)-alumina with water added as the dispersing medium. For the
PVA binder, the MOF powder was instead added to a solution of
ethanol solution containing a polymer mixture of polyvinyl groups
such as polyvinyl alcohol and polyvinyl butyral. The resulting
mixture was shaped into beads using a hand-made pan granulator.
During the process, the spheres were sprayed with the respective
solvent in order to achieve desired size. The beads were then sieved
and rolled using a roller machine to enhance their spherical
shape. Finally, the prepared samples were dried at \SI{303}{\kelvin}
for \SI{12}{\hour} to remove all residual solvent.
The resulting beads were near spherical in shape, with a diameter
between \SIrange{2}{2.5}{\milli\metre}.

\subsection{Characterisation of powders and pellets}

The primary interest of the study was observing differences
in adsorption properties between the powder and the shaped materials.

Thermogravimetric analysis was used to verify that the binder
did not change the thermal stability of the materials and, in the
case of the PVA variant, to ensure that the activation temperature
chosen did not induce polymer decomposition. The TGA method is described
in detail in Appendix~\ref{appx:char:TGA}.

The bulk and skeletal density of the powder and pellets were measured
to allow isotherms to be presented on a volume basis, as well as
to check the level of densification afforded through the
shaping process. The procedure is described in Appendix~\ref{appx:char:bulkdensity} and Appendix~\ref{appx:char:truedensity}.

Specific surface area and pore volume were determined through
nitrogen adsorption at \SI{77}{\kelvin}. These measurements were
recorded according to the method in Appendix~\ref{appx:char:N2phys}.
For inspecting changes in surface hydrophobicity, water and
methanol adsorption isotherms were measured according to
the method presented in Appendix~\ref{appx:char:vapourphys}.

Finally, all calorimetry data was recorded using the high sensitivity
Tian-Calvet calorimeter coupled with adsorption volumetry, as
introduced in \autoref{calo}.

\subsection{Sample activation for adsorption}

The materials were pre-treated before all adsorption experiments by
activation at high temperature under secondary vacuum for 16 hours.
The activation temperature was specific
to each solid: \SI{200}{\degreeCelsius} for UiO-66(Zr),
\SI{150}{\degreeCelsius} for MIL-100(Fe) and \SI{150}{\degreeCelsius}
for MIL-127(Fe).
