% !TEX root = ../../main.tex

\section{Results and discussion}

\input{\thisch/rd-tga}
\input{\thisch/rd-n2phys}

\subsection{Room temperature gas adsorption and microcalorimetry}

As previously shown in \autoref{calo},
combining microcalorimetry with adsorption manometry
can give an insight into the energetics of the
adsorption process by directly measuring differential enthalpy.
Even though the different contributions to the overall enthalpy curve
cannot be decoupled from the individual sources, such as guest-host
interactions or fluid-fluid interactions, it can be successfully
applied to observing the effect of a process or treatment such as shaping
on the properties of a MOF.

Eight probe gasses have been chosen for adsorption at \SI{303}{\kelvin}:
\ce{N2}, \ce{CO}, \ce{CO2}, \ce{CH4}, \ce{C2H6}, \ce{C3H6},
\ce{C3H8} and \ce{C4H10}.
The range of adsorbates chosen allows different effects to be investigated.
The adsorption of saturated hydrocarbons with an increasing
carbon number (C1-C4) can be
assumed to be driven strictly by Van-der-Waals forces,
due to the shielding effects of the hydrogen atoms.
Differences in the maximum uptakes of these gasses will point to
loss of porosity or crystalinity. A capacity loss with
an increasing carbon number will point to size exclusion effects
induced by the binder, such as particle coating, pore filling or
pore obstruction.
The other probes have been chosen for their properties which can
shine light on other specific interaction types
present during the adsorption.
Carbon monoxide is a slightly dipolar molecule which has the
ability to interact with other charges in the pores.
It also can highlight CUS (coordinatively unsaturated sites)
generated through defects, reduction or open metal sites due to its
propensity for \( \pi \) backbonding coordination.
This electron transfer process can also result in complexation with
molecular orbitals in systems with \( \pi \) bonds such as alkenes 
and alkynes.
Propylene is used as an unsaturated hydrocarbon probe gas for this purpose.
Carbon dioxide is a highly quadrupolar molecule which will be
strongly adsorbed in polar pore environments. Changes in the adsorption
behaviour of \ce{CO2} will shed light on such surface changes and
can even be used as a predictor
of hydrophobicity~\cite{chanutScreeningEffectWater2017}.
Finally, \ce{N2} is a staple adsorptive for material characterisation
when used at \SI{77}{\kelvin}. The molecule is a slight quadrupole
and has also been shown to chelate to some transitional metals in
an analogue fashion to \ce{CO}.

To eliminate the influence of kinetic and diffusion effects on the 
experiments, care has been taken to allow time for complete equilibration
of both pressure and calorimeter signal.
The complete dataset of adsorption isotherms, on the basis of both mass
and volume can be found in \autoref{appx:shaping}.

After collecting the combined isotherm and enthalpy data, three
indicators have been chosen to best represent the effects of shaping:
initial enthalpy of adsorption, initial Henry constant and maximum capacity.
These numeric performance indicators have been calculated using the
available functionality in pyGAPS.

The initial enthalpy of adsorption extrapolated at zero coverage is
a measure of the interaction with highest energetic sites on the MOF
surface. Conversely, the initial Henry constant (\(K_{Hi}\)), here 
obtained through fitting the virial adsorption model as laid out in
\autoref{pyg:models:virial}, is also an indication of adsorption in
the pores before any
layering or adsorbate-adsorbate interaction comes into effect.
The last indicator, maximum capacity, was taken as the loading attained when
the isotherm reached a plateau. In the case of probes where the plateau
was outside the range of pressure of the instrumentation (>\SI{50}{\bar}),
the loading at the highest available pressure was considered as a
suitable approximation.
The three key performance indicators (\gls{KPI}) have then been compared side by
side on both the powder and shaped samples.

\input{\thisch/rd-calo-uio66}
\input{\thisch/rd-calo-mil100}
\input{\thisch/rd-calo-mil127}

\input{\thisch/rd-vapour}